### 2018-02-02 Sections/essay_the_quantum_space_race.tex
Very minor

>>>>

\comment{Constellation of satellites reaching line-of-sight with every point on Earth, much like the GPS network. This will initially form a quantum repeater network which performs a single task -- Bell-pair distribution. This will incorporate both entanglement swapping and entanglement purification, yielding a genuine global-scale quantum repeater network.}

\comment{Figure of satellite constellation}
